\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-10-01 gwnnDraft02.tex
more small things.

Applying this to the standard reheating scenario of $N$natrualness, introduced in~\ref{sec:reheat}, we get GW signals as seen in figure~(\ref{fig::Nnatural}). Plotted are the individual contributions to the signal from each phase transitioned sector, as well as the coherent sum of all sectors. Future GW interferometers and pulsar timing array sensitivity curves are shown in comparison to the signal. The sensitivity curves are interpreted as the region of possible detection if intersected with the GW signal, more detail in the construction of these curves is given in Section~\ref{sec:detection}. Notice that the total signal is dominated by the first sectors contribution. This is caused by the quartic temperature ratio suppression in Eq.~(\ref{eq:alpha}) and the large temperature gaps between adjacent sectors. Such a suppression leads to standard $N$natrualness evading future detector thresholds by a few orders of magnitude in units of energy density.

@@

The GW results of these cases are presented in figure~(\ref{fig:Haa}). In all cases, the summed GW signal is detectable by one or more proposed interferometers. When relaxing the assumptions on $\beta/H$, the scenarios in figure~(\ref{fig:Haa}) are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$ The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors. As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.  This is seen in figure~(\ref{fig:Haa}), where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum. The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature). Eventually, a temperature limit will be reached where two (or multiple) distinct peaks will be visible, provided that the amplitudes are comparable. 

@@

The spectral noise curves used to create the PLI curves shown in figures~(\ref{fig::Nnatural}) and ~(\ref{fig:Haa}) where taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and ~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array. We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.

>>>>

Applying this to the standard reheating scenario of $N$natrualness, introduced in~\ref{sec:reheat}, we get GW signals as seen in Fig.~\ref{fig::Nnatural}. Plotted are the individual contributions to the signal from each phase transitioned sector, as well as the coherent sum of all sectors. Future GW interferometers and pulsar timing array sensitivity curves are shown in comparison to the signal. The sensitivity curves are interpreted as the region of possible detection if intersected with the GW signal, more detail in the construction of these curves is given in Section~\ref{sec:detection}. Notice that the total signal is dominated by the first sectors contribution. This is caused by the quartic temperature ratio suppression in Eq.~(\ref{eq:alpha}) and the large temperature gaps between adjacent sectors. Such a suppression leads to standard $N$natrualness evading future detector thresholds by a few orders of magnitude in units of energy density.

@@

The GW results of these cases are presented in Fig.~\ref{fig:Haa}. In all cases, the summed GW signal is detectable by one or more proposed interferometers. When relaxing the assumptions on $\beta/H$, the scenarios in Fig.~\ref{fig:Haa} are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$ The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors. As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.  This is seen in Fig.~\ref{fig:Haa}, where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum. The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature). Eventually, a temperature limit will be reached where two (or multiple) distinct peaks will be visible, provided that the amplitudes are comparable. 

@@

The spectral noise curves used to create the PLI curves shown in Figs.~\ref{fig::Nnatural} and \ref{fig:Haa} were taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and ~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array. We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.
